Covariate analysis of ROSMAP Reprocessed RNASeq

### 2016-05-20 code/Rmd/ROSMAP_RNASeq_Reprocessed.Rmd
Minor modifications

---
title: "Covariate analysis of ROSMAP RNASeq"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(knitr)
library(knit2synapse)
library(synapseClient)

@@

knit2synapse::knitToFolderEntity(file = "./ROSMAP_RNASeq.Rmd",
                                 parentId ="syn5570291",
                                 entityName = 'ROSMAP RNASeq Reprocessed Counts (Based on cogdx)')
```

@@

# Sex
vcd::mosaic(~ msex + cogdx, data = COVARIATES)
```

### CPM Normalisation
Preprocess counts matrix and metadata. Determine design matrix for normalisation and differential expression analysis.

Remove genes that have less than 1 cpm counts in at least 50% of samples.
```{r cpmnormalisation, cache=TRUE}
PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(COUNT,MIN_GENE_CPM=1, MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
```
### Normalisation (with NULL)
Initial normalisation usign voom (with NULL design)
```{r initial.voom.normalisation}
# Initial normalisation of gene expression
VOOM.GENE_EXPRESSION = voom(PROCESSED_COUNTS$filteredExprMatrix, design=NULL, plot=T)
```
### Outlier analysis
Clustering of initial normalised data (with NULL design)
```{r decompse.normalise.data, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(VOOM.GENE_EXPRESSION$E, scale.=T, center = T)

>>>>

---
title: "Covariate analysis of ROSMAP Reprocessed RNASeq"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(knitr)
library(knit2synapse)
library(synapseClient)

@@

knit2synapse::knitToFolderEntity(file = "./ROSMAP_RNASeq_Reprocessed.Rmd",
                                 parentId ="syn5570291",
                                 entityName = 'ROSMAP RNASeq Reprocessed Counts (Based on cogdx)')
```

@@

# Sex
vcd::mosaic(~ msex + cogdx, data = COVARIATES)
```
### CPM Normalisation
Preprocess counts matrix and metadata. Determine design matrix for normalisation and differential expression analysis.

Remove genes that have less than 1 cpm counts in at least 50% of samples.
```{r cpmnormalisation, cache=TRUE}
PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(COUNT,MIN_GENE_CPM=1, MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
```
### Normalisation (with NULL)
Initial normalisation usign voom (with NULL design)
```{r initial.voom.normalisation}
# Initial normalisation of gene expression
VOOM.GENE_EXPRESSION = voom(PROCESSED_COUNTS$filteredExprMatrix, design=NULL, plot=T)
```
### Outlier analysis
Clustering of voom adjusted data (with NULL design)
```{r decompse.normalise.data, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(VOOM.GENE_EXPRESSION$E, scale.=T, center = T)
